\documentclass{article}
\usepackage{dipole}
%\usepackage{showkeys}

\begin{document}
\title{Bipolar comparison}
\author{Nina Lebedeva, Anton Petrunin and Vladimir Zolotov}

\nofootnote{The first author was partially supported by RFBR grant 17-01-00128, 
the second author was partially supported by NSF grant DMS 1309340,
the third author was supported in part by DFG grant SPP 2026 and RFBR grant 17-01-00128.}


\newcommand{\Addresses}{{\bigskip\footnotesize

  Nina Lebedeva, \par\nopagebreak\textsc{Math. Dept.
St. Petersburg State University,
Universitetsky pr., 28, 
Stary Peterhof, 
198504, Russia.}
  \par\nopagebreak
  \textsc{Steklov Institute,
27 Fontanka, St. Petersburg, 
191023, Russia.}
  \par\nopagebreak
  \textit{Email}: \texttt{lebed@pdmi.ras.ru}

\medskip

  Anton Petrunin, \par\nopagebreak\textsc{Math. Dept. PSU, University Park, PA 16802, USA}
  \par\nopagebreak
  \textit{Email}: \texttt{petrunin@math.psu.edu}
}}

\date{}

\maketitle

\begin{abstract}
We define the so called tree comparison --- a type of metric comparison which generalize the Alexandrov comparison and defined in a similar fashion.
This type of comparison turns out to have strong connections to continuity of optimal transport between regular measures on a Riemannian manifold, in particular to the so called MTW condition introduced by Xi-Nan Ma, Neil Trudinger and Xu-Jia Wang.

\end{abstract}

\input{defs.tex}
\input{kirszbraun.tex}
\input{6-dipole.tex}
\input{convexity.tex}
\input{mtw.tex}
\input{polypole.tex}
\input{end.tex}




\begin{thebibliography}{52}
\bibitem{AKP} S. Alexander, V. Kapovitch, A. Petrunin, 
\emph{Alexandrov meets Kirszbraun.} 
Proceedings of the Gökova Geometry-Topology Conference 2010, 88--109, Int. Press, Somerville, MA, 2011.

\bibitem{AKP-book} S. Alexander, V. Kapovitch, and A. Petrunin, \emph{Alexandrov geometry.} book in preparation.

\bibitem{berg-nikolaev} Berg, I. D.; Nikolaev, I. G., \emph{Quasilinearization and curvature of Aleksandrov spaces.} Geom. Dedicata 133 (2008), 195--218.


\bibitem{FRV-Nec+Suf} Figalli, A.; Rifford, L.; Villani, C.,
\emph{Necessary and sufficient conditions for continuity of optimal transport maps on Riemannian manifolds.} Tohoku Math. J. (2) 63 (2011)

\bibitem{karcher}
Karcher, H.,
\emph{Schnittort und konvexe Mengen in vollständigen Riemannschen Mannigfaltigkeiten.}
Math. Ann. 177 1968 105--121.

\bibitem{kim-mccann} Kim, Y.-H.; McCann, R.,
\emph{Towards the smoothness of optimal maps on Riemannian submersions and Riemannian products (of round spheres in particular).}
J. Reine Angew. Math. 664 (2012), 1--27. 

\bibitem{LS}  Lang, U.; Schroeder, V.,
\emph{Kirszbraun's theorem and metric spaces of bounded curvature.}
Geom. Funct. Anal. 7 (1997), no. 3, 535–560. 

\bibitem{lebedeva-petrunin} Lebedeva, N., Petrunin, A., \emph{Curvature bounded below: a definition a la Berg--Nikolaev.} Electron. Res. Announc. Math. Sci. 17 (2010), 122--124.

\bibitem{loeper}
Loeper, G.,
\emph{On the regularity of solutions of optimal transportation problems.}
Acta Math. 202 (2009), no. 2, 241–283. 

\bibitem{MTW}  Ma, X.-N.; Trudinger, N.  Wang, X.-J.,
\emph{Regularity of potential functions of the optimal transportation problem.}
Arch. Ration. Mech. Anal. 177 (2005), no. 2, 151--183. 

\bibitem{naor}  Naor, A., \emph{An introduction to the Ribe program.} Jpn. J. Math., 7(2):167--233, 2012.

\bibitem{ohta}  Ohta, S.-I.,
\emph{Markov type of Alexandrov spaces of non-negative curvature.} Mathematika, 55(1-2):177--189, 2009.

\bibitem{petrunin} Petrunin, A., \emph{In search of a five-point Aleksandrov type condition.}  St. Petersburg Math. J. 29 (2018), no. 1.

\bibitem{perelman-petrunin} Perelman, G.; Petrunin, A., \emph{Extremal subsets in Aleksandrov spaces and the generalized Liberman theorem.} St. Petersburg Math. J. 5 (1994), no. 1, 215--227.

\bibitem{sato} Sato, T., \emph{An alternative proof of Berg and Nikolaev’s characterization of CAT(0)-spaces via quadrilateral inequality.} Arch. Math. (Basel), 93(5):  487--490, 2009.

\bibitem{sturm}  Sturm, K. T., \emph{Metric spaces of lower bounded curvature.} Exposition. Math., 17(1):35–47, 1999.


\bibitem{terng-thorbergsson}  Terng, C.-L.,  Thorbergsson, G.
\emph{Submanifold geometry in symmetric spaces.} J. Differential Geom. 42 (1995), no. 3, 665--718.

\bibitem{MTW+CTIL+} Villani, C., \emph{Regularity of optimal transport and cut locus: from nonsmooth analysis to geometry to smooth analysis.} Discrete Contin. Dyn. Syst. 30 (2011), no. 2, 559–571. 
 
\bibitem{MTW+CTIL} Villani, C., \emph{Stability of a 4th-order curvature condition arising in optimal transport theory.}
J. Funct. Anal. 255 (2008), no. 9, 2683--2708.

 
\bibitem{villani}  Villani, C. \emph{Optimal transport. Old and new.} Grundlehren der Mathematischen Wissenschaften 338. Springer-Verlag, Berlin, 2009.
\end{thebibliography}


%\input{7-dipole.tex}
\Addresses
\end{document}
